Optimising Heterogeneous Ambulance Fleet Allocations in Jakarta

### 2025-01-29 tex/main.tex
include confidence intervals and write up confidence intervals for grids

Running the simulation and MESLMHPHF objective function of expected survival for
both the current and the two proposed grid allocations gives the results shown
in Table~\ref{tbl:current_grid_results}. The simulation was run over half a
year, with a month warm up time, over eight replications. 
\textcolor{red}{The variability over the eight replications ...}
We observe that the
two proposed grid allocations perform much worse than the current allocation as
measured by mean response time, survival, and percentage of calls abandoned.
This is expected as vehicle numbers are lower under the new proposals, as well
as the allocations focussing on coverage rather than response times or survival.

\begin{table}
\begin{tabular}{rrrr}
\toprule
Allocation & Baseline & Grid 3km & Grid 5km \\
\midrule
Number of EAs & 81 & 70 & 71 \\
Number of RRVs & 13 & 0 & 0 \\
Ambulance Utilisation & 30.99\% & 36.58\% & 35.79\% \\
RRV Utilisation & 22.47\% & - & - \\
Mean Response Time (mins) & 17.69 & 22.29 & 24.05 \\
StDev Response Time (mins) & 6.98 & 8.02 & 7.94 \\
MESLMHPHF Objective & 98.34\% & 87.95\% & 85.64\% \\
Expected A1 Survival & 26.05\% & 13.64\% & 12.23\% \\
Percent Abandoned & 0.00\% & 0.52\% & 0.93\% \\
\bottomrule
\end{tabular}
\caption{Calculated KPIs for the current and proposed grid allocations.}
\label{tbl:current_grid_results}
\end{table}

@@

Table~\ref{tbl:current_optimal_compare} compares the MESLMHPHF objective
function value and simulation derived KPIs between the current and the optimised
allocations, for each demand scenario. It can be seen that, as expected, as
demand increases then utilisation of primary and secondary vehicles increase, as
the ambulance service is busier. Similarly, mean response time increases with
demand, this is due to the vehicles being busier, and therefore less chance that
the most optimally placed vehicle is dispatched. This is confirmed by the
percentage of calls abandoned increasing with demand, showing ambulance
unavailability.

@@

Figures~\ref{fig:results_objective_single}-\ref{fig:results_abandoned_multiple}
display the obtained KPIs for each of these allocations. Confidence intervals
over the eight replications were too small to display on the plots. It can
immediately be seen that increasing the resource level has a positive effect on
all KPIs, with vehicle utilisations, mean response times, and percentage
abandoned decreasing, and overall survival increasing. Similarly, as expected
increasing the demand of emergency calls has a negative impact on all KPIs.

>>>>

Running the simulation and MESLMHPHF objective function of expected survival for
both the current and the two proposed grid allocations gives the results shown
in Table~\ref{tbl:current_grid_results}. The simulation was run over half a
year, with a month warm up time, over five replications. 
\textcolor{red}{The variability over the replications is very small, and we have included 90\% conficence intervals around the mean response times to demonstrate this.}
We observe that the
two proposed grid allocations perform much worse than the current allocation as
measured by mean response time, survival, and percentage of calls abandoned.
This is expected as vehicle numbers are lower under the new proposals, as well
as the allocations focussing on coverage rather than response times or survival.

\begin{table}
\begin{tabular}{rrrr}
\toprule
Allocation & Baseline & Grid 3km & Grid 5km \\
\midrule
Number of EAs & 81 & 70 & 71 \\
Number of RRVs & 13 & 0 & 0 \\
Ambulance Utilisation & 30.99\% & 36.58\% & 35.79\% \\
RRV Utilisation & 22.47\% & - & - \\[1.5mm]
\multirow{2}{*}{Mean Response Time (mins)} & 17.69 & 22.29 & 24.05 \\
 & \textcolor{red}{($\pm$ 0.07)} & \textcolor{red}{($\pm$ 0.06)} & \textcolor{red}{($\pm$ 0.03)} \\[1.5mm]
StDev Response Time (mins) & 6.98 & 8.02 & 7.94 \\
MESLMHPHF Objective & 98.34\% & 87.95\% & 85.64\% \\
MESLMHPHF A1 Objective & 26.05\% & 13.64\% & 12.23\% \\
Percent Abandoned & 0.00\% & 0.52\% & 0.93\% \\
\bottomrule
\end{tabular}
\caption{Calculated KPIs for the current and proposed grid allocations.}
\label{tbl:current_grid_results}
\end{table}

@@

Table~\ref{tbl:current_optimal_compare} compares the MESLMHPHF objective
function value and simulation derived KPIs between the current and the optimised
allocations, for each demand scenario\textcolor{red}{, along with 90\% confidence intervals over the trials}. It can be seen that, as expected, as
demand increases then utilisation of primary and secondary vehicles increase, as
the ambulance service is busier. Similarly, mean response time increases with
demand, this is due to the vehicles being busier, and therefore less chance that
the most optimally placed vehicle is dispatched. This is confirmed by the
percentage of calls abandoned increasing with demand, showing ambulance
unavailability.

@@

Figures~\ref{fig:results_objective_single}-\ref{fig:results_abandoned_multiple}
display the obtained KPIs for each of these allocations. Confidence intervals
over the replications were too small to display on the plots. It can
immediately be seen that increasing the resource level has a positive effect on
all KPIs, with vehicle utilisations, mean response times, and percentage
abandoned decreasing, and overall survival increasing. Similarly, as expected
increasing the demand of emergency calls has a negative impact on all KPIs.
